*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-03 Code/Manuscript_O2.Rmd
Added more ref to figures

Our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)C).  Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~]. For distinct fits for different photoperiod fits refer to figure \@ref(fig:PhotoperiodPurFitsPlots)C.

@@

\newpage
XXXXEdit text depending upon which ocean protein figures we useXXXXX
Ocean detections of proteins mediating protein metabolism support this interpretation of distinct FtsH function across clades of *P. marinus*. Ribosome proteins from clade HLI MED4, clade LLIII SS120 and clade LLIV MIT9313 show generally similar patterns vs. [O~2~] and depth, a proxy for peak PAR.  FtsH3, inferred to mediate PSI assembly, likewise shows a similar pattern between MED4 and MIT9313.  But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.  Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~], suggesting limited requirement for protein turnover under low [O~2~].

>>>>

As with MED4 and SS120, our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)C).  Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~]. For distinct fits for different photoperiod fits refer to figure \@ref(fig:PhotoperiodPurFitsPlots)C.

@@

\newpage
XXXXEdit text depending upon which ocean protein figures we useXXXXX
Ocean detections of proteins mediating protein metabolism support this interpretation of distinct FtsH function across clades of *P. marinus*. Ribosome proteins from clade HLI MED4, clade LLIII SS120 and clade LLIV MIT9313 show generally similar patterns vs. [O~2~] and depth, a proxy for peak PAR  (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)).  FtsH3, inferred to mediate PSI assembly, likewise shows a similar pattern between MED4 and MIT9313 (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)).  But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.  Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~] (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)), suggesting limited requirement for protein turnover under low [O~2~].
